Removal only

### 2020-05-29 analysis/figure-4.Rmd
fig 3 with new infographic

e <- plotcandidatetiming(hypvsd, "HTR2C", " ") + theme(axis.title.x = element_blank()) + labs(y = NULL, subtitle = " ", title = " ") 
f <- plotcandidatetiming(pitvsd, "PRL", "pituitary")+ theme(axis.title.x = element_blank(), strip.text = element_blank()) + labs(y = NULL, subtitle = " ", title = " ") 
g <- plotcandidatetiming(gonvsd, "ESR2", "gonads") + theme(strip.text = element_blank()) + labs(y = NULL, subtitle = " ", title = " ") 
boxplots2 <- plot_grid(e,f,g, nrow = 3)
boxplots2
```

>>>>

e <- plotcandidatetiming(hypvsd, "HTR2C", " ") + theme(axis.title.x = element_blank()) + labs(y = NULL, subtitle = " ", title = " ") 
f <- plotcandidatetiming(pitvsd, "PRL", "pituitary")+ theme(axis.title.x = element_blank(), strip.text = element_blank()) + labs(y = NULL, subtitle = " ", title = " ") 
g <- plotcandidatetiming(gonvsd, "ESR2", "gonads") + theme(strip.text = element_blank()) + labs(y = NULL, subtitle = " ", title = " ") 
boxplots2 <- plot_grid(e,f,g, nrow = 3)
```
